Efficiently Handling Guards in the low level design of RPython's tracing JIT

### 2012-07-25 talk/vmil2012/paper.tex
fix capitalization
add code to build backend data tables about machine code and guard data sizes and add the latest results
move the figure and caption definition from the table template to the paper
start explaining the contents of the tables

\include{figures/benchmarks_table}

>>>>

The following analysis is based on a selection of benchmarks taken from the set
of benchmarks used to measure the performance of PyPy as can be seen
on\footnote{http://speed.pypy.org/}. The selection is based on the following
criteria \bivab{??}. The benchmarks were taken from the PyPy benchmarks
repository using revision
\texttt{ff7b35837d0f}\footnote{https://bitbucket.org/pypy/benchmarks/src/ff7b35837d0f}.
The benchmarks were run on a version of PyPy based on the
tag~\texttt{release-1.9} and patched to collect additional data about the
guards in the machine code
backends\footnote{https://bitbucket.org/pypy/pypy/src/release-1.9}. All
benchmark data was collected on a MacBook Pro 64 bit running Max OS
10.7.4 \bivab{do we need more data for this kind of benchmarks} with the loop
unrolling optimization disabled\bivab{rationale?}.

Figure~\ref{fig:ops_count} shows the total number of operations that are
recorded during tracing for each of the benchmarks on what percentage of these
are guards. Figure~\ref{fig:ops_count} also shows the number of operations left
after performing the different trace optimizations done by the trace optimizer,
such as xxx. The last columns show the overall optimization rate and the
optimization rate specific for guard operations, showing what percentage of the
operations was removed during the optimizations phase.

\begin{figure*}
    \include{figures/benchmarks_table}
    \caption{Benchmark Results}
    \label{fig:ops_count}
\end{figure*}

\bivab{should we rather count the trampolines as part of the guard data instead
of counting it as part of the instructions}

Figure~\ref{fig:backend_data} shows
the total memory consumption of the code and of the data generated by the machine code
backend for the different benchmarks mentioned above. Meaning the operations
left after optimization take the space shown in Figure~\ref{fig:backend_data}
after being compiled. Also the additional data stored for the guards to be used
in case of a bailout and attaching a bridge.
\begin{figure*}
    \include{figures/backend_table}
    \caption{Total size of generated machine code and guard data}
    \label{fig:backend_data}
\end{figure*}

Both figures do not take into account garbage collection. Pieces of machine
code can be globally invalidated or just become cold again. In both cases the
generated machine code and the related data is garbage collected. The figures
show the total amount of operations that are evaluated by the JIT and the
total amount of code and data that is generated from the optimized traces.
